### 2021-07-02 doc/src/MSLevel.tex
Reduce chances for unfortunate page breaks

The local interrupts currently defined by the Advanced Interrupt
Architecture are listed here, in order of decreasing default priority:
\begin{displayLinesTable}[l@{\quad}l]
30 & Reserved for standard reporting of bus or system errors \\
58 & Tentatively reserved for per-core high-power/over-temperature events \\
54 & Reserved for standard high-priority RAS events \\
\noalign{\bigskip}
38 & Reserved for standard low-priority RAS events \\
18 & Debug/trace interrupt \\
\end{displayLinesTable}
\emph{RAS} is an abbreviation for \emph{Reliability, Availability, and
Serviceability}.

@@

Machine-level CSR \z{mtopi} is read-only with width MXLEN.
A read of \z{mtopi} returns information about the highest-priority
pending-and-enabled interrupt for machine level, in this format:
\begin{displayLinesTable}[l@{\quad}l]
bits 27:16 & IID \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{mtopi} are reserved and read as zeros.

@@

Supervisor-level CSR \z{stopi} is read-only with width SXLEN.
A read of \z{stopi} returns information about the highest-priority
pending-and-enabled interrupt for supervisor level, in this format:
\begin{displayLinesTable}[l@{\quad}l]
bits 27:16 & IID \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{stopi} are reserved and read as zeros.

>>>>

The local interrupts currently defined by the Advanced Interrupt
Architecture are listed here, in order of decreasing default
priority:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
30 & Reserved for standard reporting of bus or system errors \\
58 & Tentatively reserved for per-core high-power/over-temperature events \\
54 & Reserved for standard high-priority RAS events \\
\noalign{\bigskip}
38 & Reserved for standard low-priority RAS events \\
18 & Debug/trace interrupt \\
\end{displayLinesTable}
\emph{RAS} is an abbreviation for \emph{Reliability, Availability, and
Serviceability}.

@@

Machine-level CSR \z{mtopi} is read-only with width MXLEN.
A read of \z{mtopi} returns information about the highest-priority
pending-and-enabled interrupt for machine level, in this
format:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 27:16 & IID \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{mtopi} are reserved and read as zeros.

@@

Supervisor-level CSR \z{stopi} is read-only with width SXLEN.
A read of \z{stopi} returns information about the highest-priority
pending-and-enabled interrupt for supervisor level, in this
format:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 27:16 & IID \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{stopi} are reserved and read as zeros.
